The effect of restricted substrate diffusion on microbial community function and structure

### 2019-06-11 SI_code.Rmd
Figs. 2 and 3 changed

```{r vegan analysis, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
#Bacteria
bac.norm<-decostand(bac, method=c("normalize"))
bac.dist<-vegdist(bac.norm, method = "jaccard")
bac.ad<-adonis(bac.dist~Substrate+Structure/Substrate, bac_env, strata = bac_env$Day)

#Fungi
fungi.norm<-decostand(fungi, method=c("normalize"))
fungi.dist<-vegdist(fungi.norm, method = "jaccard")
fungi.ad<-adonis(fungi.dist~Substrate+Structure/Substrate, fungi_env, strata = fungi_env$Day)

>>>>

```{r vegan analysis, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
#Bacteria
bac.norm<-decostand(bac, method=c("normalize"))
bac.dist<-vegdist(bac.norm, method = "bray")
bac.ad<-adonis(bac.dist~Substrate+Structure/Substrate, bac_env, strata = bac_env$Day)

#Fungi
fungi.norm<-decostand(fungi, method=c("normalize"))
fungi.dist<-vegdist(fungi.norm, method = "bray")
fungi.ad<-adonis(fungi.dist~Substrate+Structure/Substrate, fungi_env, strata = fungi_env$Day)
